### 2019-03-04 report/final-report.tex
Checkpoint

We have implemented our synthesis algorithms in
of OCaml and integrated them into Boomerang system,
where they are available as open source code~\cite{GitHub}.
Users of Boomerang can write lenses by hand, specify them as
synthesis tasks, or do a combination of both.

We have analyzed our algorithms theoretically, proving various
soundness and completeness results.  We have also analyzed our
algorithms empirically, studying their impact on a range of real and
synthetic benchmarks.  Our full results have been published in a
series of conference papers and technical
reports~\cite{bijective-synthesis,quotient-synthesis,symmetric-synthesis}.  In the rest of this
section, we summarize some of the key results.

@@

We first study the effectiveness of the pure bijective synthesis
algorithm by evaluating its performance on a set of 39
benchmark programs.  
%
All evaluations were performed on a 2.5 GHz Intel Core i7 processor with 16 GB
of 1600 MHz DDR3 running macOS Sierra.

\paragraph*{Benchmark Suite Construction}
We constructed our benchmarks primarily by adapting examples from
Augeas~\cite{augeas} and 
Flash Fill~\cite{gulwani-popl-2014}.
%
Augeas is a configuration editing system for Linux that uses lens
combinators similar to those in Boomerang. However, it transforms
strings on the left to structured trees on the right rather than
transforming strings to strings.
We adapted these Augeas lenses to our setting by converting the
right-hand sides to strings that correspond to serialized versions
of the tree formats.  
We derived 29 of the benchmark tests by
adapting the first 27 lenses in alphabetical order, as well as the lenses
\CF{aug/xml-firstlevel} and \CF{aug/xml} that were referenced
by the `A' lenses.
Furthermore, the 12 last synthesis problems derived
from Augeas were tested after \Optician{} was
finalized, demonstrating that the optimizations were not
overtuned to perform well on the testing data.
%
Flash Fill is a system that allows users to specify common string
transformations by example~\cite{gulwani-popl-2014}.  
We derived three benchmarks from the first few examples in the
paper and one from the running example on
extracting phone numbers.

Both Augeas and Flash Fill permit non-bijective transformations.
To test our system on these benchmarks, we had to convert them into
bijective transformations by hand.  More specifically, in many of the
benchmarks, we normalized
the whitespace in the documents so the amount of whitespace was equal
in the source and target.  In a few of the benchmarks, either the
source or the target was missing information present in the other
format.  We modified those benchmarks by adding the missing
information back into the file.

Finally, we added custom examples to highlight weaknesses of
our algorithm (\CF{cap-prob} and \CF{2-cap-prob}) 
and to test situations for which we thought the tool would be
particularly useful (\CF{workitem-probs}, \CF{date-probs}, \CF{bib-prob},
and \CF{addr-probs}).   These examples convert between work item formats, date
formats, bibliography formats, and address formats, respectively.

>>>>

We implemented our synthesis algorithms in the OCaml programming language
and integrated them into Boomerang system, where they are available as open
source code~\cite{GitHub}\bcp{Two more pointers needed}.  Users of Boomerang
can write lenses by hand, specify them as synthesis tasks, or do a
combination of both.

We analyzed our algorithms theoretically, proving various soundness and
completeness results.  We also analyzed these algorithms empirically,
studying their impact on a range of real and synthetic benchmarks.  Our
results have been published in a series of conference papers and technical
reports~\cite{bijective-synthesis,quotient-synthesis,symmetric-synthesis}.
In the rest of this section, we summarize key results.

@@

We first show the effectiveness of the pure bijective synthesis
algorithm by evaluating its performance on a set of 39
benchmark programs.  
%
All evaluations were performed on a 2.5 GHz Intel Core i7 processor with 16 GB
of 1600 MHz DDR3 running macOS Sierra.

\paragraph*{Benchmark Suite Construction}
We constructed our benchmarks primarily by adapting examples from
Augeas~\cite{augeas} and 
Flash Fill~\cite{gulwani-popl-2014}.
%
Augeas is a configuration editing system for Linux that uses lens
combinators similar to those in Boomerang.  
% , with some small
% differences. However, it transforms 
% strings on the left to structured trees on the right rather than
% transforming strings to strings.
% We adapted these Augeas lenses to our setting by converting the
% right-hand sides to strings that correspond to serialized versions
% of the tree formats
We derived 29 of the benchmark tests by
adapting the first 27 lenses from the Augeas library in alphabetical order,
as well as the lenses 
\CF{aug/xml-firstlevel} and \CF{aug/xml} that were referenced
by the `A' lenses.
Furthermore, the 12 last synthesis problems derived
from Augeas were tested after our synthesizer was was
finalized, demonstrating that the optimizations were not
over-tuned to perform well on the testing data.
%
Flash Fill is a system that allows users to specify common string
transformations by example~\cite{gulwani-popl-2014}.  
We derived three benchmarks from the first few examples in this
paper and one from the running example on
extracting phone numbers.

Both Augeas and Flash Fill permit non-bijective transformations.
To test our system on these benchmarks, we had to convert them into
bijective transformations (by hand).  Specifically, in many of the
benchmarks, we normalized
the whitespace in the documents so the amount of whitespace was equal
in the source and target.  In a few of the benchmarks, either the
source or the target was missing information present in the other
format.  We modified those benchmarks by adding the missing
information back into the file.

Finally, we added a few custom examples designed to highlight known
weaknesses of our algorithm
%(\CF{cap-prob} and \CF{2-cap-prob}) 
and to test situations for which we thought the tool would be
particularly useful.
% (\CF{workitem-probs}, \CF{date-probs}, \CF{bib-prob},
% and \CF{addr-probs}).
These examples convert between work item formats, date
formats, bibliography formats, and address formats, respectively.
